---
title: "Inspect Data"
editor_options: 
  chunk_output_type: console
---


# Inspect Data

```{r}
suppressPackageStartupMessages(library(tidyverse))
library(targets)
library(tarchetypes)
library(DT)
```

```{r, eval = TRUE}
knitr::opts_knit$set(root.dir = "../../")
```

## Modelling Matrix

- `category_id` contains the ID of the clinical impact factor.
- `activity_id_new` contains the ID of the audit/inspection
- `has_finding` specifies whether there was a finding of the specific impact factor at the specific audit/inspection

### Original
```{r}
df_mm <- tar_read(df_mm)

df_mm %>%
  select(category_id, activity_id_new, has_finding, everything())

df_mm %>%
  filter(lubridate::year(start_date) <= 2019) %>%
  group_by(category_id) %>%
  summarise(n_activities = n_distinct(activity_id_new)) %>%
  knitr::kable()

tibble(columns = colnames(df_mm)) %>%
  DT::datatable()
```

### Binned
```{r}
df_mm_bin <- tar_read(df_mm_bin)

df_mm_bin %>%
  select(category_id, activity_id_new, has_finding, everything())


tibble(columns = colnames(df_mm_bin)) %>%
  DT::datatable()
```

## Coefficients

Modelling coefficients have been preselected by a combination of EDA and SME input.

```{r}
tar_read(df_form) %>%
  DT::datatable()
```

## Cross Validation Indeces

Indeces of modelling matrix that define time series cross validation strategy.

```{r}
tar_read(df_cv)
```

## Lookup Tables

### Features

All names of all features and their variations.

```{r}
tar_read(df_feat_lookup) %>%
  DT::datatable()
```

### Categories

All finding statements mapped to clinical impact factors.

```{r}
tar_read(df_cat_lookup) %>%
  DT::datatable()
```

